# Copyright 2025 European Medicines Agency
#
# This software is developed by the DARWIN EU Coordination Centre
#
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
#
#     http://www.apache.org/licenses/LICENSE-2.0
#
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.
#
# This study code contains unmodified open-source dependencies.

---
title: "Frailty Polypharmacy Results Analysis"
author: "Adam Black"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load data}

library(dplyr)
dbdir <- file.path("results", "results_combined.duckdb")
con <- DBI::dbConnect(duckdb::duckdb(), dbdir = dbdir)

# DBI::dbListTables(con)

# cohorts <- tbl(con, "cohort_counts") %>% collect
# demo <- tbl(con, "demographics")  %>% collect
prev <- tbl(con, "prevalence") %>% collect
# hosp <- tbl(con, "hospitalization_death") %>% collect
# cohort_attrition <- tbl(con, "cohort_attrition") %>% collect
# drugs <- tbl(con, "ls_drugs") %>% collect 
# conditions <- tbl(con, "ls_conditions") %>% collect 

```


```{r}

df <- prev %>% 
  filter(strata_level == "overall") %>% 
  select(cdm_name, variable_name, estimate_name, estimate_value, cohort = group_level) %>%
  filter(stringr::str_detect(variable_name, "frailty"), variable_name != "frailty_category") %>% 
  tidyr::pivot_wider(names_from = "estimate_name", values_from = "estimate_value") %>% 
  mutate(count = as.numeric(count), percentage = as.numeric(percentage))


library(ggplot2)

plt <- ggplot(df, aes(x = variable_name, y = percentage, color = cdm_name)) +
  geom_point() +
  facet_wrap(~cohort) +
  # facet_grid(cdm_name ~ cohort) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



plotly::ggplotly(plt)
```


```{r}
DBI::dbDisconnect(con, shutdown = T)
```

